### 2018-03-27 project.tex
Update
Numbers 8, 13, 15, 16, 17, 18 editted

	\begin{theorem}
		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
	\end{theorem}
	\begin{proof}
	$\tau$ is $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace$. So $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \subseteq \mathcal{P}(X)$. $\emptyset, X \in \tau$ because for $\mathcal{B}' = \emptyset, \bigcup \mathcal{B}' = \emptyset$ and for $\mathcal{B}' = X, \bigcup \mathcal{B}' = X$. Let $\mathcal{U} \subseteq \tau$ and $\bigcup \mathcal{U} \in \tau$ because for each $U \in \mathcal{U}, U = \bigcup \mathcal{B}_{U}'$ for some $\mathcal{B}_{U}' \subseteq \mathcal{B}$ So, $\bigcup \mathcal{U} = \bigcup \lbrace \bigcup \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace$. Let $\mathcal{B}' = \bigcup \lbrace \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace.$ So, $\bigcup \mathcal{U} = \bigcup \mathcal{B}'.$ \newline For $U, V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace, U = B_1$ and $V = B_2, B_1, B_2 \in \mathcal{B}$ such that $B_1 = \mathcal{B}$ and $B_2 = \mathcal{B}$. Then $U \cap V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \supseteq W$ so there exists $x \in V, U : x \in U \cap V \supseteq W$. Therefore $x \in W \subseteq U \cap V \in \tau$.
	\end{proof}

	\begin{theorem}
	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ generates $\tau$ if:
	\newline
	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
	\newline
	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
\end{theorem}
\begin{proof}:\newline
	\begin{enumerate}
		\item For $x \in U \in \tau$, let $B = \lbrace x \rbrace$, so $x \in B \subseteq U \in \tau$.
		\item $B_1, B_2 \in \mathcal{B}$. Let $B_3 = (B_1 \cap B_2)$, so $B_3 \subseteq (B_1 \cap B_2)$. Since $x \in (B_1 \cap B_2)$, $x \in B_3$. Thus, $x \in B_3 \subseteq (B_1 \cap B_2)$.
	\end{enumerate}
\end{proof}

	\begin{theorem}
	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
	\end{theorem}
	\begin{proof}:\newline
	\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = X$.
	\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$ so $B_1 = B_2 = \lbrace y \rbrace$. Let $B_3 = \lbrace y \rbrace$ so $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2 = \lbrace y \rbrace$. 
		\end{enumerate}
	\end{proof}

@@

	\begin{theorem}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{R}\rbrace$ is a basis.
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2$ so $ x \in B_3$.
		\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace (a, b) : a<b \in \mathbb{Q}\rbrace$. Let $x$, $y \in \mathbb{Q}$ and let $B = (x-y, x+y)$, so $B \subseteq \mathbb{Q}$ and $x \in B \in \mathcal{B}$.
		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$. $a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$. Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$. So, $x \in B_3 \subseteq B_1 \cap B_2$.
		\end{enumerate} 
	\end{proof}

@@

	\begin{proof}
		$K_1$ and $K_2$ are compact so $\bigcup \mathcal{U}_1 \supseteq K_1$ and $\mathcal{U}_2 \supseteq K_2$. $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$. $K_3 = K_1 \cup K_2$. Also, for finite $\mathcal{F}_1 \subseteq \mathcal{U}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2, \bigcup \mathcal{F}_1 \supseteq K_1 and \bigcup \mathcal{F}_2 \supseteq K_2$. So, $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_1 \cup K_2$. Thus, $K_1 \cup K_2$ is compact.
	\end{proof}

@@

	\begin{proof}

	As shown previously, when $K$ is compact there is $\mathcal{U}$ such that $\bigcup \mathcal{U} \supseteq K$. Also, there is a finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$. For $F \in \mathcal{F}$, we can find an open covering $\mathcal{U}' \subseteq \mathcal{U}$ such that $\mathcal{U}' \supseteq F$. Also, we can find a finite $\mathcal{F}' \subseteq \mathcal{U}'$ such that $\bigcup \mathcal{F}' \supseteq F$.
	\end{proof}

@@

	\begin{proof}
		$K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace$. Let $\mathcal{U} = \lbrace (n, n+1) : -1 < n < 2 \rbrace$. Then $\bigcup \mathcal{U} \supseteq K$. Now, there are clearly finitely many $F \in \mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$.
	\end{proof}

	\begin{proposition}
	  Any unbounded subset of \(\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
		For a subset to be compact it must be bounded by definition. An unbounded $K \subseteq \mathbb{R}$ cannot be compact because there is no finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$ because $K$ itself is not bound so it is impossible for $\bigcup \mathcal{F} \supseteq K$. Thus $K$ cannot be compact.
	\end{proof}

	\begin{proposition}
	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
		By the same argument, an open interval $(a, b)$ is not bounded, and therefore not compact. For every open cover $\mathcal{U}$ of $(a, b)$ has infinitely many $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq (a, b)$. So there are not finitely many $F \in \mathcal{F}$ and $(a, b)$ is not compact.
	\end{proof}

@@

	\begin{theorem}
		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
	\end{theorem}
	\begin{proof}
		$K_{n \in \mathbb{N}}$ are countable since $\mathbb{N}$ is countable. If $K = \bigcup_{n \in \mathbb{N}} K_n$, then $\bigcup_{n \in \mathbb{N}} K_n \supseteq K$.
	\end{proof}

@@

	\begin{theorem}
		Every hemicompact subset of a topological space is \(\sigma\)-compact.
	\end{theorem}
	\begin{proof}
		By definition of $\sigma$-compact, we have compact subspaces $K_n$ such that for $\sigma$-compact $K'$, $K' = \bigcup_{n \in \mathbb{N}} K_n$. Obviously, for any subset $H$ of the hemicompact set $K$, $H \subseteq K_n \subseteq K$ and since $K' = \bigcup_{n \in \mathbb{N}} K_n, H \subseteq K'$.
	\end{proof}

>>>>

	\begin{theorem}
		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
	\end{theorem}
	\begin{proof} NEEDS WORK\newline
	$\tau$ is $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace$. So $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \subseteq \mathcal{P}(X)$. $\emptyset, X \in \tau$ because for $\mathcal{B}' = \emptyset, \bigcup \mathcal{B}' = \emptyset$ and for $\mathcal{B}' = X, \bigcup \mathcal{B}' = X$. Let $\mathcal{U} \subseteq \tau$ and $\bigcup \mathcal{U} \in \tau$ because for each $U \in \mathcal{U}, U = \bigcup \mathcal{B}_{U}'$ for some $\mathcal{B}_{U}' \subseteq \mathcal{B}$ So, $\bigcup \mathcal{U} = \bigcup \lbrace \bigcup \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace$. Let $\mathcal{B}' = \bigcup \lbrace \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace.$ So, $\bigcup \mathcal{U} = \bigcup \mathcal{B}'.$ \newline For $U, V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace, U = B_1$ and $V = B_2, B_1, B_2 \in \mathcal{B}$ such that $B_1 = \mathcal{B}$ and $B_2 = \mathcal{B}$. Then $U \cap V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \supseteq W$ so there exists $x \in V, U : x \in U \cap V \supseteq W$. Therefore $x \in W \subseteq U \cap V \in \tau$.
	\end{proof}

	\begin{theorem}
	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ generates $\tau$ if:
	\newline
	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
	\newline
	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
\end{theorem}
\begin{proof}:\newline
	\begin{enumerate}
		\item For $x \in \mathbb{X} \in \tau$, select $x \in B \in \mathcal{B}$, so $x \in \mathbb{X}$ and $x \in B$, then $x \in B \subseteq \mathbb{X} \in \tau$.
		\item See definition 6-2.
		\item Let $\mathcal{B'} \subseteq \mathcal{B}$ and $\mathcal{B'} = \mathcal{B}$ ,so $\bigcup \mathcal{B'} = \bigcup \mathcal{B} = \tau$.
	\end{enumerate}
\end{proof}

	\begin{theorem}
	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
	\end{theorem}
	\begin{proof}:\newline
	\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
	\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
		\end{enumerate}
	\end{proof}

@@

	\begin{theorem}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{R}\rbrace$ is a basis.
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $x \in B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2$ so $ x \in B_3$.
		\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\llcorner x \lrcorner -1 < x < \ulcorner x \urcorner + 1$. Let B = $(\llcorner x \lrcorner -1, \ulcorner x \urcorner + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$. $a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$. Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$. So, $x \in B_3 \subseteq B_1 \cap B_2$.
		\end{enumerate} 
	\end{proof}

@@

	\begin{proof}
	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_1$ and $\mathcal{U}_2$ be open covers of $K_1$ and$K_2$ respectively. So $\bigcup \mathcal{U}_1 \supseteq K_1$, and $\bigcup \mathcal{U}_2 \supseteq K_2$ and $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$. $K_3 = K_1 \cup K_2$. There is a $\mathcal{U}_3 \supseteq K_3$. So let $\mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{U}_2 = \mathcal{U}_3$. For finite $\mathcal{F}_3 \subseteq \mathcal{U}_3, \mathcal{F}_3 \supseteq K_3$, so $\mathcal{F}_3 \supseteq K_1 \cup K_2$. Let $\mathcal{F}_1 = \mathcal{F}_3$ and $\mathcal{F}_2 = \mathcal{F}_3$, so $K_1 \cup K_2$ is compact.
	\end{proof}

@@

	\begin{proof}
	For $F = \lbrace x_i : 0 \leq x_i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering on $F$ so $\bigcup \mathcal{U} \supseteq F$. Then we can find  a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq F$. Suppose $\mathcal{U}_0 = \lbrace x_0 : -1 \leq x_0 < n+1 \rbrace \subseteq \mathcal{U}$ then let $\mathcal{F} = \mathcal{U}_0$, so $\bigcup \mathcal{F} \supseteq F$.
	\end{proof}

@@

	\begin{proof}
	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering on $K$ such that $\bigcup \mathcal{U} \supseteq K$. So for $\mathcal{U}_0 \subseteq \mathcal{U}, \mathcal{U}_0 = \lbrace n_0 : -1 \leq n_0 \leq 2, n_0 \in \mathbb{Z} \rbrace$. $\bigcup \mathcal{U}_0 \supseteq K$. So, let finite $\mathcal{F} = \mathcal{U}_0$, so $\mathcal{F} \subseteq \mathcal{U}$ and $\mathcal{F} \supseteq K$.
	\end{proof}

	\begin{proposition}
	  Any unbounded subset of \(\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
	For unbounded $K \subseteq \mathbb{R}$ suppose there is an open covering $\mathcal{U}$ on $K$. Then there exists a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$. For $\mathcal{F}$ to be finite it must be bounded. So, there is no $\bigcup \mathcal{F} \supseteq K$. Essentially we would need $\mathcal{F} = \lbrace (- \infty , n) : n \in \mathbb{Z^-} \rbrace \cup \lbrace (n-3, \infty) : n \in \mathbb{Z^+} \rbrace$ which is not finite.
	\end{proof}

	\begin{proposition}
	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
	\end{proof}

@@

	\begin{theorem}
		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
	\end{theorem}
	\begin{proof}
	\end{proof}

@@

	\begin{theorem}
		Every hemicompact subset of a topological space is \(\sigma\)-compact.
	\end{theorem}
	\begin{proof}
		This proof is trivial as it is defined as stated here in definition 21.
	\end{proof}
